---
title: "Booktitle"
subtitle: "A Fitting Subtitle (Or Not)"
author:
    - Maik Thalmann^[Georg-August-University Göttingen, maik.thalmann@gmail.com]
date: "Göttingen, `r format(Sys.time(), '%d %B, %Y')`"
publishers: "Georg-August-University Göttingen"
subject: "Linguistics"
titlehead: "Some Titlehead"
contact: https://mkthalmann.github.io/home/
fontsize: 11pt
output:
 pdf_document:
    toc: true
    pandoc_args: 
        - "--highlight=tango"
        - "--top-level-division=part"
    template: template.tex
    citation_package: biblatex
    keep_tex: true
    latex_engine: xelatex
    dev: cairo_pdf
documentclass: scrartcl
bibliography: ../bibliographyuni.bib
mainfont: XITS
sansfont: "Source Sans Pro"
monofont: "Hack"
mathfont: "Asana Math"
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
options(scipen = 999)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, comment=NA)
knitr::opts_chunk$set(fig.path='figs/', fig.align = 'center', fig.asp = 0.6, 
    out.width = '80%')
knitr::opts_chunk$set(tidy = "styler", tidy.opts = list(scope = "tokens"))
packages <- c("here", "tidyverse", "knitr", "kableExtra", "hrbrthemes")
xfun::pkg_attach(packages, install = TRUE)

# nicer plots
theme_maik <- function() {
    theme_ipsum_rc() %+replace%
        theme(
            panel.grid.major.x = element_blank(),
            panel.grid.minor.x = element_blank(),
            panel.grid.major.y = element_line(colour = 'gray'),
            panel.grid.minor.y = element_line(colour = 'gray'),
            panel.spacing = unit(.5, "lines"),
            plot.margin = unit(c(.1, .1, .1, .1), "cm"),
            axis.line = element_line(colour = 'gray', size = .5),
            strip.text.x = element_text(size = 9, color = "white"),
        ) +
        theme(
            axis.title.x = element_text(size = 12),
            axis.title.y = element_text(size = 12))
}
```

# Experiment Description

## Author(s)

* Musterfrau, Eva; Mustermann, Max & Mustermensch, CJ

## Design

### Independent Variables

 \textsc{Factor1} $\times$ \textsc{Factor2}

* Factor1 (within-items, within-subjects): bla, bli
* Factor2 (within-items, within-subjects): blu, blo

### Dependent Variables

* Judgments [1 \ldots 7], Reaction Times, 2AFC [option1, option2], \ldots

## Participants

* Number of participants:
* Participant information we need to collect
    * Major
    * Age
    * Native Language
    * \ldots
* Eligibility criteria for participants
    * non-biblingual
    * Students (18 to 28 y/o, from Göttingen)
    * \ldots
* Reimbursement

## Materials 

* Number of critical items
* Number of filler/control items
* randomized/pseudo-randomized
* text/audio stimuli (who's doing the recording)

### Critical items

\begin{exe}
    \ex \begin{xlist}
        \ex Example Sentence
        \ex Example Sentence
        \ex Example Sentence
        \ex Example Sentence
    \end{xlist}
\end{exe}

What are going to control (hold constant)?

* Number
* Gender
* Syllable length
* \ldots

### Fillers/Controls

\begin{exe}
    \ex \begin{xlist}
        \ex Type

        Example Sentence
        \ex Type

        Example Sentence
    \end{xlist}
\end{exe}

## Procedure

* How is the data collected?
* What is the experimental setup?

## Hypothesis

* Hypothesis in words (main effects, interactions, a priori contrasts
* Statistical methods (LMM, ANOVA, \ldots); exepected equivalence (TOST)
* Why do we expect that result (previous results/studies, theoretical assumptions, \ldots)

### Plot

```{r data, echo = TRUE}
d <- tibble(
    factor1 = c("bla", "bla", "bli", "bli"),
    factor2 = c("blu", "blo", "blu", "blo"),
    judgment = c(7, 4, 5, 1)
)

kable(d, booktabs = T) %>%
  kable_styling(position = "center")
```

```{r mean-lines}
ggplot(d, aes(x = factor1, y = judgment, pch = factor2, color = factor2, group = factor2)) +
    geom_point() +
    geom_line() +
    theme_maik() +
    scale_color_grey()
```

```{r freq-bars}
ggplot(d, aes(x = factor1, y = judgment, fill = factor2, color = factor2)) +
    geom_col(alpha = .5, position = position_dodge(width = 1)) +
    theme_maik() +
    scale_color_grey() +
    scale_fill_grey()
```

### Contrasts (if applicable)

* List them here [@heimkratzer1998semantics]

### Checklist

\begin{todolist}
  \item[\done] We can be sure that the participants understood the items.

  How? 

  \item X

  \item[\wontfix] Y
\end{todolist}

# Details

## Introductory Text/recording

@tarski1944semantic

@dayal2009variation